Java Sorting Algorithms Comparison

### 2015-02-23 Programming Project B/paper.tex
added available invarariants to the paper up to a point

@@

\textbf{Merge Together Second While Loop Invariant}:

%% TODO: Add pre and post conditions here
A heap sort can be implemented in a variety of languages using the pseudocode below in Algorithm 3.
\newline
\begin{algorithm}
\caption {\textsc{Heap-Sort}(A)}
\label{algo:heapsort}
\begin{algorithmic}[1]
\Procedure{Heapify}{A, i, total}
\State{$var$ $left = i * 2$}
\State{$var$ $right = left + 1$}
\State{$var$ $iPrime = i$}
\If{$left <= total$ and $A[left] > A[i]$}
	\State{$i = left$}
\EndIf
\If{$right <= total$ and $A[right] > A[i]$}
	\State{$i = right$}
\EndIf
\If{$i != iPrime$}
	\State{$var$ $temp = A[iPrime]$}
	\State{$A[iPrime] = A[i]$}
	\State{$A[i] = tmp$}
	\State{$A = heapify(A, i, total)$}
\EndIf
\State{\Return{$A$}}
\EndProcedure
\Procedure{Heap-Sort}{A}
\State{$var$ $size = A.length$}
\For{$var$ $i = size / 2$ downto $1$}
	\State{$A = heapify(A, i, size$}
\EndFor
\For{$var$ $i = size$ downto $1$}
	\State{$var$ $tmp = A[1]$}
	\State{$A[0] = A[i]$}
	\State{$A[i] = tmp$}
	\State{$size = size - 1$}
	\State{$A = heapify(A, 1, size)$}
\EndFor
\State{\Return{$A$}}
\EndProcedure
\end{algorithmic}
\end{algorithm}
%% END PROCEDURE

>>>>

\textbf{Merge Sort Conclusion}: %%TODO: Write this

@@

\textbf{Merge Together Second While Loop Invariant}: Combined contains x number of elements where $x >= i$ and those elements are contained in left[0 ... i] in stricly non-decreasing order.
\textbf{Merge Together Second While Loop Invariant Initialization}: The invariant holds true before the first iteration of the loop because x has been incremented when i has been incremented and elements have been added to combined from left if and only if $left[i] < right[y]$ and from right if and only if $left[i] >= right[y]$.
\textbf{Merge Together Second While Loop Invariant Maintenance}: The invariant holds true at the beginning of each iteration of the loop because x has been incremented when i has been incremented and elements have been added to combined from left in order.
\textbf{Merge Together Second While Loop Invariant Termination}: The invariant holds true at the termination of the loop because x has been incremented when i has been incremented and elements have been added to combined from left in order.
\textbf{Merge Together Third While Loop Invariant}: Combined contains x number of elements where x is greather than or equal to y and those elements are contained in right[0 ... y] in stricly non-decreasing order.
\textbf{Merge Together Third While Loop Invariant Initialization}: The invariant holds true before the first initialization of the loop because x has been incremented when y has been incremented and elements have been added to combined from left if and only if $left[i] < right[y]$ and from right if and only if $left[i] >= right[y]$.
\textbf{Merge Together Third While Loop Invariant Maintenance}: The invariant holds true at the beginning of each iteration of the loop because x has been incremented when y has been incremented and elements have been added to combined from right in order.
\textbf{Merge Together Third While Loop Invariant Termination}: The invariant holds true at the termination of the loop because x has been incremented when y has been incremented and elements have been added to combined from right in order.
\textbf{Merge Together Conclusion}: %%TODO: Write this.

A heap sort can be implemented in a variety of languages using the pseudocode below in Algorithm 3.
\newline
\textbf{Heap Sort Pre-Condition}: A is a non-empty array with a natural order.
\newline
\textbf{Heap Sort Post-Condition}: A' is a permutation of A in strictly non-decreasing order.
\newline
\textbf{Heapify Pre-Condition}: A is a non-empty array with a comparable data type in a natural order.
\newline
\textbf{Heapify Post-Condition}: %%TODO: Write this.
\newline
\begin{algorithm}
\caption {\textsc{Heap-Sort}(A)}
\label{algo:heapsort}
\begin{algorithmic}[1]
\Procedure{Heapify}{A, i, total}
\State{$var$ $left = i * 2$}
\State{$var$ $right = left + 1$}
\State{$var$ $iPrime = i$}
\If{$left <= total$ and $A[left] > A[i]$}
	\State{$i = left$}
\EndIf
\If{$right <= total$ and $A[right] > A[i]$}
	\State{$i = right$}
\EndIf
\If{$i != iPrime$}
	\State{$var$ $temp = A[iPrime]$}
	\State{$A[iPrime] = A[i]$}
	\State{$A[i] = tmp$}
	\State{$A = heapify(A, i, total)$}
\EndIf
\State{\Return{$A$}}
\EndProcedure
\Procedure{Heap-Sort}{A}
\State{$var$ $size = A.length$}
\For{$var$ $i = size / 2$ downto $1$}
	\State{$A = heapify(A, i, size$}
\EndFor
\For{$var$ $i = size$ downto $1$}
	\State{$var$ $tmp = A[1]$}
	\State{$A[0] = A[i]$}
	\State{$A[i] = tmp$}
	\State{$size = size - 1$}
	\State{$A = heapify(A, 1, size)$}
\EndFor
\State{\Return{$A$}}
\EndProcedure
\end{algorithmic}
\end{algorithm}
%% END PROCEDURE
